Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-04-13 papers/ms.tex
update ms

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{\today}
\revised{---}
\accepted{---}
%\submitjournal{AAS Journals}
\shorttitle{Trio of Mini-Neptunes in Cep-Her}

@@

\title{
  %Three Mini-Neptunes in a 40 Million Year Old Behemoth
  Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association
  %Three Mini-Neptunes, 40 to 50 Million Years Old 
  %A Trio of 40 to 50 Million Year Old Mini-Neptunes
}

@@

% 208 words (250 max)
\begin{abstract}
  Stellar positions and velocities from Gaia are yielding a refined
  view of open cluster dispersal.  Here we present an analysis of a
  group stars spanning Cepheus ($l=100^\circ$) to Hercules
  ($l=40^\circ$), hereafter the Cep-Her complex.
  The group includes four Kepler Objects of Interest:
  Kepler-1643 b ($R_{\rm p} = 2.32 \pm 0.14\,R_\oplus$, $P = 5.3\ {\rm days}$),
  KOI-7368 b ($R_{\rm p} = 2.22 \pm 0.12\,R_\oplus$, $P = 6.8\ {\rm days}$), 
  KOI-7913 Ab ($R_{\rm p} = 2.34 \pm 0.18\,R_\oplus$, $P = 24.2\ {\rm days}$), and
  Kepler-1627 Ab ($R_{\rm p} = 3.85 \pm 0.11\,R_\oplus$, $P = 7.2\ {\rm days}$).
  The latter Neptune-sized planet is in part of the Cep-Her
  complex called the $\delta$\ Lyr\ cluster
  \citep{bouma_kep1627_2022}.  Here we focus on the former three
  systems, which are in other regions of the association.  Based on
  kinematic evidence from Gaia, stellar rotation periods from TESS,
  and spectroscopy, these three objects are also $\approx$40 million
  years (Myr) old.  More specifically, we find that Kepler-1643 is
  $46^{+9}_{-7}$\,Myr old, based on its membership in a dense
  sub-cluster of the complex called RSG-5.  KOI-7368 and KOI-7913 are
  $36^{+10}_{-8}$\,Myr old, and are in a diffuse region that we call
  CH-2.  Based on the transit shapes and high resolution imaging, all
  three objects are most likely planets, with false positive
  probabilities of $6\times10^{-9}$, $4\times10^{-3}$, and
  $1\times10^{-4}$ for Kepler-1643, KOI-7368, and KOI-7913
  respectively.  These planets empirically demonstrate that
  mini-Neptunes with sizes of $\sim$2 Earth radii exist at ages of
  40 million years.
\end{abstract}

@@

% * Main text <3500 words (not including acknowledgements, appendices, or other
%   supplementary)

@@

In this work, we leverage recent analyses of the Gaia data, which have
greatly expanded our knowledge of stellar groups \citep[{\it
e.g.},][]{CantatGaudin2018a,KounkelCovey2019,Kerr2021}.  To date these
analyses have mostly clustered on stellar positions and 2-D
velocities.  One important result has been the discovery of
diffuse streams and tidal tails comparable in stellar mass to the
previously known cores of nearby open clusters
\citep{meingast_psceri_2019,Meingast2021,gagne_number_2021}.  Even
though these streams are spread over tens to hundreds of
parsecs, their velocity dispersions can remain coherent at the
$\sim$1\kms\ level.  Internal dynamics and projection effects can also
drive them to be much larger: in the Hyades,
stars in the tidal tails are expected to span up to $\pm 40\mkms$ in velocity
relative to the cluster center \citep{jerabkova_800_2021}.
The stars in such diffuse regions can be verified to be the same age
as the core members through analyses of
color-absolute magnitude diagrams \citep{KounkelCovey2019}, stellar
rotation periods \citep{curtis_tess_2019,bouma_2021_ngc2516}, and
chemical abundances \citep{hawkins_2020}.  While there are 
implications for our understanding of star formation and cluster
evolution \citep{dinnbier_tidal_2020}, a separate consequence is that
we now know the ages of many more stars, including previously known
planet hosts.

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
  {\bf Positions and velocities of candidate members of the Cep-Her
  complex.}
  {\it Top row}: On-sky positions in galactic coordinates.  Black
  points are stars for which group membership is more secure than for
  gray points.  Kepler-1627 is in the outskirts of the $\delta$ Lyr
  cluster \citep{bouma_kep1627_2022}, which is centered at $\{ l, b\}
  \approx \{ 66^\circ, 12^\circ\}$.
  {\it Middle row}: Galactic positions.  The Sun is at $\{X, Y, Z\} =
  \{0, 0, 20.8\}$\,pc; lines of constant heliocentric distance are
  shown between 250 and 400\,pc, spaced by 50\,pc.
  {\it Bottom row}: Galactic tangential velocities (left) and
  galactic longitudinal velocity versus galactic longitude (right).
  The gray band in the lower-right shows the $\pm$1-$\sigma$
  projection of the Solar velocity with respect to the local standard
  of rest.  There is a strong spatial and kinematic overlap between
  Kepler-1643 and RSG-5 (magenta).  The local population
  of candidate young stars around KOI-7368 and KOI-7913 is more
  diffuse -- we call this region ``CH-2'' (lime-green).
  The selection method for the black, gray, purple, and green points
  is described in Section~\ref{subsec:members}.
	\label{fig:XYZvtang}
	}
\end{figure*}

@@

Our focus is on a region of the Galaxy approximately 200 to 500\,pc
from the Sun, above the galactic plane, and spanning galactic
longitudes of roughly $40^\circ$ to $100^\circ$.  Two rich
clusters in this region are the $\delta$~Lyra cluster
\citep{stephenson_possible_1959} and RSG-5 \citep{roser_nine_2016}.
Each of these clusters was known before Gaia.  Their reported ages
between 30 and 60\,Myr.  Early empirical
evidence that these two clusters could be part of a large and more
diffuse population was apparent in the Gaia-based photometric analysis
of pre-main-sequence stars by \citet[][see their Figures~11
and~13]{Zari2018}.  Further kinematic connections and complexity were
highlighted by \citet{KounkelCovey2019}, who included these previously
known groups in the larger structures dubbed ``Theia~73'' and
``Theia~96''\footnote{See their visualization online at
\url{http://mkounkel.com/mw3d/mw2d.html} (accessed 15 March 2022)}.
The connection made by \citet{KounkelCovey2019} between the previously
known open clusters and the other groups in the region was made as
part of an unsupervised clustering analysis of the Gaia DR2 positions
and on-sky velocities with a subsequent manual ``stitching'' step.
Their results support the idea that there is an overdensity of
30 to 60\,Myr old stars in this region of
the Galaxy.  \citet{Kerr2021}, in a volume-limited analysis of the
Gaia DR2 point-source catalog out to one third of a kiloparsec,
identified three of the nearest sub-populations, dubbed
``Cepheus-Cygnus'', ``Lyra'', and ``Cerberus''.  \citet{Kerr2021}
reported ages for each of these subgroups between 30 and 35 Myr.

@@

Color-absolute magnitude diagrams (CAMDs) of the candidate RSG-5 and
CH-2 members are shown in the upper row of Figure~\ref{fig:age}.  The
stars from the $\delta$~Lyr cluster are from
\citet{bouma_kep1627_2022}, and the field stars are from the Gaia EDR3
Catalog of Nearby Stars \citep{gaia_gcns_2021}.  To make these
diagrams, we imposed the data filtering criteria from
\citet[][Appendix B]{GaiaCollaboration2018}, which 
include binaries while omitting instrumental artifacts from for
instance low photometric signal to noise, or a small number of
visibility periods.  We then corrected for extinction using the
\citet{lallement_threedimensional_2018}\footnote{\url{https://stilism.obspm.fr/}}
dust maps and the extinction coefficients $k_X\equiv A_X/A_0$ from
\citet{GaiaCollaboration2018}, assuming that $A_0 = 3.1 E(B-V)$.  This
yielded a mean and standard deviation for the reddening of
$E(B-V)=0.036\pm0.002$ for RSG-5, and $E(B-V)=0.017\pm0.001$
for CH-2.  By way of comparison, in \citet{bouma_kep1627_2022} the
same query for the $\delta$~Lyr cluster yielded
$E(B-V)=0.032\pm0.006$.  Finally, for the plots we set the $\bpmrpo$
color range to best visualize the region of maximal age information
content: the pre-main-sequence.

The CAMDs show that for RSG-5, almost all of our candidate members are
on a tight pre-main-sequence locus.  This implies a false positive
rate of a few percent, at most.  By comparison, our control sample
(the $\delta$~Lyr candidates) has a false positive rate of
$\approx$12\%, based on the number of stars that photometrically
overlap with the field population, rather than the bulk cluster
population.  For CH-2, our membership selection gives 27 objects in
the color range displayed, and 23 of them appear to be consistent with
being on the pre-main-sequence.  This implies a false positive rate in
CH-2 of $\approx$15\%.

Figure~\ref{fig:age} also shows that most RSG-5 and
CH-2 members overlap with the $\delta$~Lyr cluster, and that the groups are therefore
roughly the same age.  To quantify this, we use the empirical method
introduced by \citet[][their Section~6.3]{gagne_mutau_2020}.  This
idea is to fit the pre-main-sequence loci of a set of
reference clusters, and to then model the locus of the target cluster
as a linear combination of these reference cluster loci.  For our
reference clusters, we used UCL, IC\,2602, and the Pleiades, with the
memberships reported by \citet{Damiani2019} and
\cite{CantatGaudin2018a} respectively.  We adopted ages of 16\,Myr for
UCL \citep{pecaut_star_2016}, 38\,Myr for IC\,2602\footnote{ Ages for
IC\,2602 vary from 40 to 46\,Myr based on lithium-depletion-boundary
(LDB) measurements \citep{dobbie_ic_2010,randich_gaiaeso_2018}, and
from 30 to 46\,Myr based on isochronal analyses
\citep{stauffer_rotational_1997,david_ages_2015,bossini_age_2019}.},
and 112\,Myr for the Pleiades \citep{dahm_2015}.  These assumptions
and the subsequent processing steps taken to exclude field stars and binaries
were identical to those
described in \citet{bouma_kep1627_2022}.  The mean and 
uncertainty of the resulting age posterior are $46^{+9}_{-7}$\,Myr for
RSG-5, and $36^{+10}_{-8}$\,Myr for CH-2.  For comparison, the this
procedure yields an age for the $\delta$~Lyr cluster of
$38^{+6}_{-5}$\,Myr.  
The slightly older isochronal age of RSG-5 is
consistent with its location
relative to the $\delta$~Lyr cluster in
the upper left panel of Figure~\ref{fig:age}.

@@

We selected stars suitable for gyrochronology by requiring $\bpmrpo
\geq 0.5$ to focus on FGKM stars that experience magnetic braking.
For TESS, we also restricted our sample to $G<16$, to ensure the stars
are bright enough to extract usable light curves from the full-frame
images (FFIs).  The magnitude cut corresponds to $\bpmrpo < 2.6$
($\sim$M3V) at the relevant distances.  These cuts gave 19 stars in
CH-2 and 42 stars in RSG-5.  We extracted light curves from the TESS
images using the \texttt{unpopular} package
\citep{hattorio_2021_cpm}, and regressed them against systematics with
its causal pixel model.  We measured rotation periods using
Lomb-Scargle periodograms and visually vetted the results using an
interactive program that allows us to switch between TESS Cycles,
select particular sectors, flag stars with multiple periods, and
correct half-period harmonics. For ZTF, we used the same color cut to
focus on FGKM stars, but restricted the sample to $13 < G < 18$ to
avoid the saturation limit on the bright end and ensure sufficient
photometric precision at the faint end. We followed the procedure
outlined in \citet{curtis_rup147_2020}: we downloaded $8'\times8'$
image cutouts, ran aperture photometry for the target and neighboring
stars identified with Gaia, and used them to define a systematics
correction to refine the target light curves.

@@

For CH-2, 13/19 stars have rotation periods that are obviously faster
than their counterparts in the Pleiades (68\%).  4 stars, not included
in the preceding numerator, are M-dwarfs with rotation periods between
10 and 12.5 days.  As just discussed, the age interpretation for these
M-dwarfs is not obvious.  Regardless, the $\approx$15\% false positive
rate determined from the CAMD seems consistent with our fraction of
detected rotation periods, given that RSG-5 was also missing rotation
period detections for $\approx$15\% of its candidate members, which
all seemed photometrically consistent with being part of a single
pre-main-sequence locus.

It is challenging to convert these stellar rotation periods to a
precise age estimate, since on the pre-main-sequence the stars are
spinning up due to thermal contraction rather than down due to
magnetized braking.  Regardless, the rotation period distributions of
both CH-2 and RSG-5 seem consistent with other 30\,Myr to 50\,Myr
clusters ({\it e.g.}, IC\,2602 and IC\,2391;
\citealt{douglas_stephanie_t_2021_5131306}).  They also seem
consistent with the estimated false positive rates determined from the
color-absolute magnitude diagrams.

@@

Some salient stellar properties of the Kepler objects in Cep-Her can
be gleaned from Figure~\ref{fig:age}.  They span spectral types of G8V
(Kepler-1627) to K6V (KOI-7913 A).  The secondary in the KOI-7913
system has spectral type $\approx$K8V.  And since a Solar-mass star
with solar metallicity arrives at the zero-age main sequence at
$t\approx40$ Myr \citep{choi_mesa_2016}, these stars are all in the
late stages of their pre-main-sequence contraction.  Their
heliocentric distances are $\approx$260\,pc (KOI-7913 and KOI-7368, in
CH-2) and $\approx$340\,pc (Kepler-1643, in RSG-5).

@@

To verify these parameters and to also analyze spectroscopic youth
proxies such as the Li\,\textsc{I} 6708\,\AA\ doublet and H$\alpha$,
we acquired spectra.  We also acquired high resolution imaging for
each system, to constrain the existence of visual companions,
including possible bound binaries.  The system-by-system details
follow, and the relevant results are also summarized in
Table~\ref{tab:sysparams}.

@@

\paragraph{Spectra}
For Kepler-1643, we acquired two iodine-free spectra from Keck/HIRES
on the nights of 2020 Aug 16 and 2021 Oct 25.  The acquisition and
analysis followed the usual techniques of the California Planet Survey
\citep{howard_cps_2010}.  We derived the stellar parameters ($T_{\rm
eff}, \log g, R_\star$) using \texttt{SpecMatch-Emp}
\citep{yee_SM_2017}, which yielded values in $<1$-$\sigma$ agreement
with those from the cluster-isochrone method.  This approach also
yielded $[{\rm Fe/H}]=0.13 \pm 0.09$.  Using the broadened synthetic
templates from \texttt{SpecMatch-Synth} \citep{petigura_cksi_2017}, we
found $v\sin i = 9.3 \pm 1.0\,\mkms$.  The systemic radial velocity at
the two sequence epochs was $-9.1 \pm 1.9\,\mkms$ and $-7.8\pm
1.2\,\mkms$ respectively.  To infer the equivalent width of the
Li\,\textsc{I} 6708\,\AA\ doublet, we followed the procedure described
by \citet{bouma_2021_ngc2516}.  This yielded a strong detection: ${\rm
EW}_{\rm Li} = 130^{+6}_{-5}$\,m\AA, with values consistent at
$<1$-$\sigma$ between the two epochs.   The quoted value does not
correct for the Fe\,\textsc{I} blend at 6707.44\AA, because HIRES
resolves the two features.

@@

\subsection{KOI-7368}
\paragraph{Spectra}
For KOI-7368, we acquired a spectrum on 2015 June 1 using the echelle
spectrograph (TRES; \citealt{furesz_tres_2008}) mounted at the
Tillinghast 1.5m at the Fred Lawrence Whipple Observatory.  The
stellar parameter classification pipeline for the TRES spectra has
been described by \citet{2021tsc2.confE.124B}.  It is based on the
synthetic template library originally constructed by
\citet{buchhave_hatp16b_class_2010}.  The resulting stellar parameters
($T_{\rm eff}, \log g, R_\star$) agreed with those from the
cluster-isochrone method within $1$-$\sigma$, though the effective
temperature was more precise by a factor of three.  Auxiliary
spectroscopic parameters included the metallicity $[{\rm Fe/H}]= -0.02
\pm 0.08$, the equatorial velocity $v\sin i = 20.21 \pm 0.50\,\mkms$,
and the systemic velocity ${\rm RV}_{\rm sys} = -10.9 \pm 0.2\,\mkms$.
The Li 6708\AA\ EW measurement procedure yielded ${\rm EW}_{\rm Li} =
236^{+16}_{-14}$\,m\AA.

\paragraph{High-Resolution Imaging}
We acquired adaptive optics imaging of KOI-7368 on the night of 2019
June 12, again using NIRC2.  The observational configuration and
reduction was identical as for Kepler-1643.  No companions were
detected, and the analysis of the image residuals yielded contrast
limits of $\Delta K' = 5.2$ mag at $\rho = 150$ mas, $\Delta K' = 6.7$
mag at $\rho = 300$ mas, and $\Delta K' = 8.7$ mag at $\rho > 1000$
mas.

@@

We have showed that Kepler-1643~b, KOI-7368~b, and KOI-7913~Ab
are 40 to 50 million years old, and that each signal
is most likely planetary.  The evidence for the planetary
interpretation comes from an application of \texttt{VESPA} to the
Kepler data, alongside new adaptive optics imaging from NIRC2.  The
validity of the \texttt{VESPA} framework rests on the premise that
non-astrophysical false positives, including false alarms and known
neighboring eclipsing binaries, can be rejected.  Kepler-1643 and
KOI-7368 both pass all but one of the canonical vetting checks: the
check for centroid offsets between the in and out-of-transit phases.
For both cases, we have argued the weak observed shifts seem to be
caused by starspot-induced variability in specific quarters
shifting the stellar center-of-light.
In addition, our imaging rules out companions stars with the necessary
brightness and position to explain the reported shifts.

>>>>

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{---}
\revised{---}
\accepted{---}
%\submitjournal{AAS Journals}
\shorttitle{Trio of Mini-Neptunes in Cep-Her}

@@

\title{
  Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association
}

@@

% 208 words (250 max)
\begin{abstract}
  Stellar positions and velocities from Gaia are yielding a new window
  on
  open cluster dispersal.  Here we present an analysis of a
  group stars spanning Cepheus ($l=100^\circ$) to Hercules
  ($l=40^\circ$), hereafter the Cep-Her complex.
  The group includes four Kepler Objects of Interest:
  Kepler-1643 b ($R_{\rm p} = 2.32 \pm 0.14\,R_\oplus$, $P = 5.3\ {\rm days}$),
  KOI-7368 b ($R_{\rm p} = 2.22 \pm 0.12\,R_\oplus$, $P = 6.8\ {\rm days}$), 
  KOI-7913 Ab ($R_{\rm p} = 2.34 \pm 0.18\,R_\oplus$, $P = 24.2\ {\rm days}$), and
  Kepler-1627 Ab ($R_{\rm p} = 3.85 \pm 0.11\,R_\oplus$, $P = 7.2\ {\rm days}$).
  The latter Neptune-sized planet is in part of the Cep-Her
  complex called the $\delta$\ Lyr\ cluster
  \citep{bouma_kep1627_2022}.  Here we focus on the former three
  systems, which are in other regions of the association.  Based on
  kinematic evidence from Gaia, stellar rotation periods from TESS,
  and spectroscopy, these three objects are also $\approx$40 million
  years (Myr) old.  More specifically, we find that Kepler-1643 is
  $46^{+9}_{-7}$\,Myr old, based on its membership in a dense
  sub-cluster of the complex called RSG-5.  KOI-7368 and KOI-7913 are
  $36^{+10}_{-8}$\,Myr old, and are in a diffuse region that we call
  CH-2.  Based on the transit shapes and high resolution imaging, all
  three objects are most likely planets, with false positive
  probabilities of $6\times10^{-9}$, $4\times10^{-3}$, and
  $1\times10^{-4}$ for Kepler-1643, KOI-7368, and KOI-7913
  respectively.  These planets empirically demonstrate that
  mini-Neptunes with sizes of $\sim$2 Earth radii exist at ages of
  40 million years.
\end{abstract}

@@

@@

In this work, we leverage recent analyses of the Gaia data, which have
greatly expanded our knowledge of stellar groups \citep[{\it
e.g.},][]{CantatGaudin2018a,KounkelCovey2019,Kerr2021}.  To date these
analyses have mostly clustered on stellar positions and 2-D
velocities.  One important result has been the discovery of
diffuse streams and tidal tails comparable in stellar mass to the
previously known cores of nearby open clusters
\citep{meingast_psceri_2019,Meingast2021,gagne_number_2021}.  Even
though these streams are spread over tens to hundreds of
parsecs, their velocity dispersions can remain coherent at the
$\sim$1\kms\ level.  Internal dynamics and projection effects can also
drive them to be much larger: in the Hyades,
stars in the tidal tails are expected to span up to $\pm 40\mkms$ in velocity
relative to the cluster center \citep{jerabkova_800_2021}.
The stars in such diffuse regions can be verified to be the same age
as the core cluster members through analyses of
color-absolute magnitude diagrams \citep{KounkelCovey2019}, stellar
rotation periods \citep{curtis_tess_2019,bouma_2021_ngc2516}, and
chemical abundances \citep{hawkins_2020}.  While there are 
implications for our understanding of star formation and cluster
evolution \citep{dinnbier_tidal_2020}, a separate consequence is that
we now know the ages of many more stars, including previously known
planet hosts.

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
  {\bf Positions and velocities of candidate members of the Cep-Her
  complex.}
  {\it Top row}: On-sky positions in galactic coordinates.  Black
  points are stars for which group membership is more secure than for
  gray points.  Kepler-1627 is in the outskirts of the $\delta$ Lyr
  cluster \citep{bouma_kep1627_2022}, which is centered at $\{ l, b\}
  \approx \{ 66^\circ, 12^\circ\}$.
  {\it Middle row}: Galactic positions.  The Sun is at $\{X, Y, Z\} =
  \{0, 0, 20.8\}$\,pc; lines of constant heliocentric distance are
  shown between 250 and 400\,pc, spaced by 50\,pc.
  {\it Bottom row}: Galactic tangential velocities (left) and
  galactic longitudinal velocity versus galactic longitude (right).
  The gray band in the lower-right shows the $\pm$1-$\sigma$
  projection of the Solar velocity with respect to the local standard
  of rest.  There is a strong spatial and kinematic overlap between
  Kepler-1643 and RSG-5 (magenta).  The local population
  of candidate young stars around KOI-7368 and KOI-7913 is more
  diffuse -- we call this region ``CH-2'' (lime-green).
  The selection method for all of the stars displayed
  is described in Section~\ref{subsec:members}.
	\label{fig:XYZvtang}
	}
\end{figure*}

@@

Our focus is on a region of the Galaxy approximately 200 to 500\,pc
from the Sun, above the galactic plane, and spanning galactic
longitudes of roughly $40^\circ$ to $100^\circ$.  Two rich
clusters in this region are the $\delta$~Lyra cluster
\citep{stephenson_possible_1959} and RSG-5 \citep{roser_nine_2016}.
Each of these clusters was known before Gaia.  Their reported ages
are between 30 and 60\,Myr.  Early empirical
evidence that these two clusters could be part of a large and more
diffuse population was apparent in the Gaia-based photometric analysis
of pre-main-sequence stars by \citet[][see their Figures~11
and~13]{Zari2018}.  Further kinematic connections and complexity were
highlighted by \citet{KounkelCovey2019}, who included these previously
known groups in the larger structures dubbed ``Theia~73'' and
``Theia~96''\footnote{See their visualization online at
\url{http://mkounkel.com/mw3d/mw2d.html} (accessed 15 March 2022)}.
The connection made by \citet{KounkelCovey2019} between the previously
known open clusters and the other groups in the region was made as
part of an unsupervised clustering analysis of the Gaia DR2 positions
and on-sky velocities with a subsequent manual ``stitching'' step.
Their results support the idea that there is an overdensity of
30 to 60\,Myr old stars in this region of
the Galaxy.  \citet{Kerr2021}, in a volume-limited analysis of the
Gaia DR2 point-source catalog out to one third of a kiloparsec,
identified three of the nearest sub-populations, dubbed
``Cepheus-Cygnus'', ``Lyra'', and ``Cerberus''.  \citet{Kerr2021}
reported ages for each of these subgroups between 30 and 35 Myr.

@@

Color-absolute magnitude diagrams (CAMDs) of the candidate RSG-5 and
CH-2 members are shown in the upper row of Figure~\ref{fig:age}.  The
stars from the $\delta$~Lyr cluster are from
\citet{bouma_kep1627_2022}, and the field stars are from the Gaia EDR3
Catalog of Nearby Stars \citep{gaia_gcns_2021}.  To make these
diagrams, we imposed the data filtering criteria from
\citet[][Appendix B]{GaiaCollaboration2018}, which 
include binaries while omitting instrumental artifacts from for
instance low photometric signal to noise, or a small number of
visibility periods.  We then corrected for extinction using the
\citet{lallement_threedimensional_2018}
dust maps\footnote{\url{https://stilism.obspm.fr/}} and the extinction coefficients $k_X\equiv A_X/A_0$ from
\citet{GaiaCollaboration2018}, assuming that $A_0 = 3.1 E(B-V)$.  This
yielded a mean and standard deviation for the reddening of
$E(B-V)=0.036\pm0.002$ for RSG-5, and $E(B-V)=0.017\pm0.001$
for CH-2.  By way of comparison, in \citet{bouma_kep1627_2022} the
same query for the $\delta$~Lyr cluster yielded
$E(B-V)=0.032\pm0.006$.  Finally, for the plots we set the
color range to best visualize the region of maximal age information
content: the pre-main-sequence.

The CAMDs show that for RSG-5, nearly all of our candidate members are
on a tight pre-main-sequence locus.  This implies a false positive
rate of a few percent, at most.  By comparison, our control sample
(the $\delta$~Lyr candidates) has a false positive rate of
$\approx$12\%, based on the number of stars that photometrically
overlap with the field population, while being outliers from the bulk cluster
population.  For CH-2, our membership selection gives 27 objects in
the color range displayed, and 23 of them appear to be consistent with
being on the pre-main-sequence.  This implies a false positive rate in
CH-2 of $\approx$15\%.

Figure~\ref{fig:age} also shows that most RSG-5 and
CH-2 members overlap with the $\delta$~Lyr cluster, and that the groups are therefore
roughly the same age.  To quantify this, we use the method
introduced by \citet[][their Section~6.3]{gagne_mutau_2020}.  The
idea is to fit the pre-main-sequence loci of a set of
reference clusters, and to then model the locus of the target cluster
as a linear combination of these reference cluster loci.  For our
reference clusters, we used UCL, IC\,2602, and the Pleiades, with the
memberships reported by \citet{Damiani2019} and
\cite{CantatGaudin2018a} respectively.  We adopted ages of 16\,Myr for
UCL \citep{pecaut_star_2016}, 38\,Myr for IC\,2602\footnote{ Ages for
IC\,2602 vary from 40 to 46\,Myr based on lithium-depletion-boundary
(LDB) measurements \citep{dobbie_ic_2010,randich_gaiaeso_2018}, and
from 30 to 46\,Myr based on isochronal analyses
\citep{stauffer_rotational_1997,david_ages_2015,bossini_age_2019}.},
and 112\,Myr for the Pleiades \citep{dahm_2015}.  These assumptions
and the subsequent processing steps taken to exclude field stars and binaries
were identical to those
described in \citet{bouma_kep1627_2022}.  The mean and 
uncertainty of the resulting age posterior are $46^{+9}_{-7}$\,Myr for
RSG-5, and $36^{+10}_{-8}$\,Myr for CH-2.  For comparison, this
procedure yields an age for the $\delta$~Lyr cluster of
$38^{+6}_{-5}$\,Myr.  
The slightly older isochronal age of RSG-5 is
consistent with its location
relative to the $\delta$~Lyr cluster in
the upper left panel of Figure~\ref{fig:age}.

@@

We selected stars suitable for gyrochronology by requiring $\bpmrpo
\geq 0.5$ to focus on FGKM stars that experience magnetic braking.
For TESS, we also restricted our sample to $G<16$, to ensure the stars
are bright enough to extract usable light curves from the full-frame
images.  The magnitude cut corresponds to $\bpmrpo < 2.6$
($\sim$M3V) at the relevant distances.  These cuts gave 19 stars in
CH-2 and 42 stars in RSG-5.  We extracted light curves from the TESS
images using the \texttt{unpopular} package
\citep{hattorio_2021_cpm}, and regressed them against systematics with
its causal pixel model.  We measured rotation periods using
Lomb-Scargle periodograms and visually vetted the results using an
interactive program that allows us to switch between TESS Cycles,
select particular sectors, flag stars with multiple periods, and
correct half-period harmonics. For ZTF, we used the same color cut to
focus on FGKM stars, but restricted the sample to $13 < G < 18$ to
avoid the saturation limit on the bright end and ensure sufficient
photometric precision at the faint end. We followed the procedure
outlined in \citet{curtis_rup147_2020}: we downloaded $8'\times8'$
image cutouts, ran aperture photometry for the target and neighboring
stars identified with Gaia, and used them to define a systematics
correction to refine the target light curves.

@@

For CH-2, 13/19 stars have rotation periods that are obviously faster
than their counterparts in the Pleiades (68\%).  4 stars, not included
in the preceding numerator, are M-dwarfs with rotation periods between
10 and 12.5 days.  As just discussed, the age interpretation for these
M-dwarfs is not obvious.  Regardless, the $\approx$15\% false positive
rate for CH-2 determined from the CAMD seems consistent with our
fraction of detected rotation periods; RSG-5 was missing
rotation periods for $\approx$15\% of its candidate members, even
though all of its stars appear photometrically consistent with being
on a single pre-main-sequence locus.

It is challenging to convert these stellar rotation periods to a
precise age estimate, since on the pre-main-sequence the stars are
spinning up due to thermal contraction rather than down due to
magnetized braking.  Regardless, the rotation period distributions of
both CH-2 and RSG-5 seem consistent with other 30\,Myr to 50\,Myr
clusters ({\it e.g.}, IC\,2602 and IC\,2391;
\citealt{douglas_stephanie_t_2021_5131306}).  They also seem
consistent with the false positive rates estimated from the
color-absolute magnitude diagrams.

@@

A few salient properties of the Kepler objects in Cep-Her can be
gleaned from Figure~\ref{fig:age}.  The stars span spectral types of
G8V (Kepler-1627) to K6V (KOI-7913 A).  The secondary in the KOI-7913
system has spectral type $\approx$K8V.  And given that a Solar-mass
star with solar metallicity arrives at the zero-age main sequence at
$t\approx40$ Myr \citep{choi_mesa_2016}, these stars are all in the
late stages of their pre-main-sequence contraction.  
% Their heliocentric distances are $\approx$260\,pc (KOI-7913 and
% KOI-7368, in CH-2) and $\approx$340\,pc (Kepler-1643, in RSG-5).

@@

To verify these parameters and to also analyze spectroscopic youth
proxies such as the Li 6708\,\AA\ doublet and H$\alpha$,
we acquired spectra.  We also acquired high resolution imaging for
each system, to constrain the existence of visual companions,
including possible bound binaries.  The system-by-system details
follow, and the relevant results are also summarized in
Table~\ref{tab:sysparams}.

@@

\paragraph{Spectra}
For Kepler-1643, we acquired two iodine-free spectra from Keck/HIRES
on the nights of 2020 Aug 16 and 2021 Oct 25.  The acquisition and
analysis followed the usual techniques of the California Planet Survey
\citep{howard_cps_2010}.  We derived the stellar parameters ($T_{\rm
eff}, \log g, R_\star$) using \texttt{SpecMatch-Emp}
\citep{yee_SM_2017}, which yielded values in $<$$1$-$\sigma$ agreement
with those from the cluster-isochrone method.  This approach also
yielded $[{\rm Fe/H}]=0.13 \pm 0.09$.  Using the broadened synthetic
templates from \texttt{SpecMatch-Synth} \citep{petigura_cksi_2017}, we
found $v\sin i = 9.3 \pm 1.0\,\mkms$.  The systemic radial velocity at
the two epochs was $-9.1 \pm 1.9\,\mkms$ and $-7.8\pm
1.2\,\mkms$ respectively.  To infer the equivalent width of the
Li\,\textsc{I} 6708\,\AA\ doublet, we followed the procedure described
by \citet{bouma_2021_ngc2516}.  This yielded a strong detection: ${\rm
EW}_{\rm Li} = 130^{+6}_{-5}$\,m\AA, with values consistent at
$<$$1$-$\sigma$ between the two epochs.   The quoted value does not
correct for the Fe\,\textsc{I} blend at 6707.44\AA, because HIRES
resolves the two features.  
Given the purported age and effective temperature of the star, the
lithium equivalent width is somewhat low.  We discuss this in greater
depth in Appendix~\ref{app:spectra}.

@@

\subsection{KOI-7368}
\paragraph{Spectra}
For KOI-7368, we acquired a spectrum on 2015 June 1 using the echelle
spectrograph (TRES; \citealt{furesz_tres_2008}) mounted at the
Tillinghast 1.5m at the Fred Lawrence Whipple Observatory.  The
stellar parameter classification pipeline for TRES has
been described by \citet{2021tsc2.confE.124B}.  It is based on the
synthetic template library constructed by
\citet{buchhave_hatp16b_class_2010}.  The resulting stellar parameters
($T_{\rm eff}, \log g, R_\star$) agreed with those from the
cluster-isochrone method within $1$-$\sigma$, though the effective
temperature was more precise by a factor of three.  Auxiliary
spectroscopic parameters included the metallicity $[{\rm Fe/H}]= -0.02
\pm 0.08$, the equatorial velocity $v\sin i = 20.21 \pm 0.50\,\mkms$,
and the systemic velocity ${\rm RV}_{\rm sys} = -10.9 \pm 0.2\,\mkms$.
The Li 6708\AA\ EW measurement procedure yielded ${\rm EW}_{\rm Li} =
236^{+16}_{-14}$\,m\AA.

\paragraph{High-Resolution Imaging}
We acquired adaptive optics imaging of KOI-7368 on the night of 2019
June 12, again using NIRC2.  The observational configuration and
reduction were identical as for Kepler-1643.  No companions were
detected, and the analysis of the image residuals yielded contrast
limits of $\Delta K' = 5.2$ mag at $\rho = 150$ mas, $\Delta K' = 6.7$
mag at $\rho = 300$ mas, and $\Delta K' = 8.7$ mag at $\rho > 1000$
mas.

@@

We have showed that Kepler-1643~b, KOI-7368~b, and KOI-7913~Ab
are 40 to 50 million years old, and that each system
is most likely planetary.  The evidence for the planetary
interpretation comes from an application of \texttt{VESPA} to the
Kepler data, alongside new imaging from NIRC2.  The
validity of the \texttt{VESPA} framework rests on the premise that
non-astrophysical false positives can be rejected.  Kepler-1643 and
KOI-7368 both pass all but one of the canonical vetting tests: the
check for centroid offsets between the in and out-of-transit phases.
For both cases, the weak observed shifts seem to be
caused by starspot-induced variability in specific quarters
spuriously moving the stellar center-of-light.
Independently, our imaging rules out companion stars at the brightness
and positions that would be needed to explain the reported shifts.

Each system has multiple indicators of youth that support the
reported ages.  For Kepler-1643, the strongest youth indicator
is its physical and kinematic association with RSG-5.  Based on the
color-absolute magnitude diagram, we are able to select members
of this cluster with a false positive rate of a few percent
(Figure~\ref{fig:age}).  Kepler-1643 is one such member.  While the stellar
rotation period period agrees with this assessment, the star's lithium
equivalent width is somewhat low, which might motivate future exploration
of lithium depletion across FGKM stars in RSG-5 (see Appendix~\ref{app:spectra})
